Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-07-23 automatica/response.tex

I believe that for this case, the K returned from completeness is 4 or 5.

The same theorem is also present in [1]. The proof, upon careful inspection, is not a proof of the statement given in the theorem. It only proves
that the reachable set is the convex set obtained by the trajectories of the corner states. However, it does not prove that if the trajectories are
safe, their convex combination is also safe. In fact, as given in the above counterexample, the vertices of polytope are safe does not mean that the
convex combination is safe.

I think this bug needs to be fixed in the BMC part of the verifier. Instead of checking the individual trajectories, you should in fact compute the
convex combination of trajectories (reachable set) and then perform the verification.}

\vspace{1em}
{\bf Response: }
%\todo[inline]{Alessandro: Response to this (Theorem 1)}
%\vspace{2em} 
Many thanks for this note. 
Notice that already in the previous manuscript we had focused on special shapes of initial and safe sets, namely (convex) hyper-boxes, which include the
origin. 
In the amended draft, we have better clarified these assumptions, and 
we have emphasised that the initial set is assumed to lie within the safe set: indeed, the contrary would trivially result in an unsafe condition. 
In conclusion, recall that the sets are hyper-boxes, thus convex, and that in view of the linear dynamics of the considered models, in practice both 
are assumed to contain the origin.

@@

\vspace{2em}
Similarly, 
\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates upper and lower
bounds for the possible trajectory of the system, up to a finite time. \rev{Considering the problem of multi-modal
dynamics,~\cite{DBLP:conf/emsoft/JhaST11} uses numerical optimization techniques to learn optimal switching logic for hybrid systems.
The last three} approaches can be placed within the research area known as ``hybrid systems theory.''  
%This technique works for both linear and non-linear systems.
The present contribution distances itself from all these cognate results.

\rev{A large body of work exists on evaluating fixed-point errors and bridging the gap between real value
and fixed-point values in synthesis in other application areas and using other
algorithmic techniques:
Genetic programming has been used to minimise the error in synthesised fixed-point programs~\cite{DBLP:conf/emsoft/DarulovaKMS13};
Smoothed proof search reduces the problem of parameter synthesis under boolean and quantitative 
objectives to a sequence of optimisation problems~\cite{DBLP:conf/popl/ChaudhuriCS14}; Synthesis of 
optimal fixed-point implementations of floating-point numerical software can be done using testing and induction~\cite{DBLP:journals/corr/abs-1302-1920}.
All of these works present potential future applications for CEGIS in synthesising implementations in fixed-point arithmetic.}

\vspace{2em}
{\bf Comment: } {\itshape 
Could you add one example to the end of Section 4 to show $R_1$, $R_2$, $R_3$, $R_4$ for a simple LTI system?

%\vspace{2em}
{\bf Comment: } {\itshape 
Section 4 is one the most interesting parts
of the paper and its current presentation is a bit sketchy. What are $m_{ij}$?} }

### 2019-08-05 automatica/response.tex

This journal submission encompasses and summarises the mentioned conference articles (CAV, HSCC, ASE) or workshop abstract (SYNTH). 
It is a more mature, complete, and comprehensive presentation of the conference material. 
Of these conference articles, the CAV/HSCC contributions provided an early presentation of the theory underlying the approach, 
whereas the ASE was a tool paper.  
The present contribution has new or updated experimental outcomes. 
The application of the CEGIS architecture to the synthesis of digital controllers for continuous plants is indeed a novel contribution of this line of
work.

\vspace{2em}
{\bf Comment: } {\itshape The results are evaluated on about a dozen and a half examples from the controls literature all with relatively small
dimensionality (2 to 5 real variables in the continuous state space), and while the authors claim the software artifacts and benchmarks are available
for evaluation, when this reviewer browsed to the link (http://www.cprover.org/DSSynth/), a page with "TBD" was shown. I did a little digging and
eventually found what I presume is the same / similar artifacts here: https://github.com/ssvlab/dsverifier and/or http://dsverifier.org/}

\vspace{1em}
{\bf Response: }

We apologise for this error and thank the reviewer for pointing it out. The DSSynth download from http://dsverifier.org/ is indeed the same code 
as our implementation for this paper, but without the experimental results and benchmarks. The correct link is now functional: http://www.cprover.org/DSSynth/journal.tar.gz.

@@

\vspace{2em}
{\bf Comment: } {\itshape Theorem 2 states completeness of the approach, specifically that there exists a finite k for which BMC can be done up-to to
provide a guarantee of future safety for all larger k' greater than k. Assuming the benchmarks all work up to some completeness threshold, I would
like to see
the completeness threshold for each benchmark in table 1. The reason being, I find this result a bit surprising in the given context (albeit not
unbelievable given the focus on LTI) and would like to see further evidence illustrating the point beyond the fairly informal proof, and it would
greatly enhance the existing discussion of timeouts, etc. related to completeness thresholds being too high for some cases.}

\vspace{1em}

{\bf Response: }

We have added the completeness threshold for each benchmark in the table. Note that the completeness threshold is dependent on the controller, 
and controllers with larger or smaller completeness thresholds may exist. Completeness thresholds of zero indicate that the the system, with the controller
selected, has only real eigenvalues.

### 2019-08-05 automatica/paper.tex
completeess thresholds and link

The CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
of the closed-loop control model model into its internal representation (IR).  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT/SMT solver to address verification checks.  We~model the 
effects of finite-precision arithmetic 
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included into
CBMC~5.7 and is available for 
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
We have further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script, 
with instructions to run all benchmarks and to reproduce our
experiments.\footnote{\url{http://www.cprover.org/DSSynth/}}
%
%\textcolor{red}{This paragraph needs to be updated by Elizabeth and Dario.}
%
%The entire implementation consists of $XXX$ and $XXX$ lines of C code in the multi-stage and abstract
%accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
%fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
%module in CEGIS CBMC.  We evaluate \tool~using $XXX$ SISO control system
%benchmarks.

@@

\begin{table*}
\centering
\begin{tabular}{| l | c | c | r | c | r |}
%
\hline
% \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
 Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time(s) & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time(s) \\\hline
Bioreact	&	2	&	8,8	&	15.35	&	10,6	&	23.76	\\
Chen	&	3	&	8,8	&	11.24	&	10,6	&	14.25	\\
Cruise 2	&	1	&	8,8	&	11.03	&	10,6	&	11.17	\\
Cruise 2	&	1	&	8,8	&	9.93	&	10,6	&	10.54	\\
cstrtmp	&	3	&	12,12	&	90.03	&	10,6	&	321.12	\\
Cstrtmp	&	2	&	8,8	&	18.56	&	10,6	&	16.99	\\
DC motor	&	2	&	8,8	&	10.34	&	10,6	&	12.32	\\
Helicopter	&	3	&	16,16	&	1116.08	&	10,6	&	168.43	\\
Inverted pendulum	&	2	&	12,12	&	16.01	&	10,6	&	18.73	\\
Magnetic pointer	&	3	&	12,12	&	1071.02	&	10,6	&	207.60	\\
Magnetic suspension	&	3	&	20,20	&	56.9	&	10,6	&	998.3	\\
Pendulum	&	2	&	8,8	&	11.74	&	10,6	&	13.69	\\
Regulator	&	5	&	10,16	&	190.28	&		&	~\xmark	\\
Satellite	&	2	&	8,8	&	13.91	&	10,6	&	16.92	\\
Spring-mass-damper	&	2	&	12,12	&	16.09	&	10,6	&	23.21	\\
Steam drum	&	3	&		&	~\xmark	&	10,16	&	21.16	\\
Supension	&	4	&	8,8	&	12.40	&	10,6	&	17.03	\\
Tape driver	&	3	&	8,8	&	12.18	&	10,6	&	14.34	\\
USCG tampa	&	3	&	12,12	&	1143.35	&	10,6	&	210.70	\\
% 
%%1  & Acrobot     & 4 & 8,8 & 61529.8\,s &  & ~\xmark \\
%% Antenna     & 6 &  & ~\xmark & 6,10 & 817.4\,s \\
%%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
% Bioreact    & 3 & 8,8 & 15.3\,s & 6,10 &23.6\,s \\
%% 
% Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 14.3\,s \\
%%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
%% Chen\_ex3   & 7 & 8,8  & 11.4\,s & 6,10 & 59.1\,s \\
%%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
% Cruise      & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s \\
%% CruiseHSCC & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s  \\
% Cstr & 3 & & ~\xmark & 6,10 & 21.4\,s \\
% Cstrtmp  & 3 & 8,8 & 12.5\,s &6,10 & 15.4\,s \\
% DCmotor   & 2 & 8,8  & 10.0\,s & 6,10 & 11.4\,s  \\
%%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
%%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
% Helicopter   & 3 &  & ~\xmark & 6,10 & 32.0\,s \\
%%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
% Invpendulum\_pendang & 2 & 8,8  & 10.7 & 6,10 & 14.8\,s\\
% Magpointer   & 2 &  & ~\xmark & 6,10 & 86.0\,s \\
% Magsuspension  & 2 & 12,12  & 39.0\,s  & 6,10 & 43.2\,s \\
% Pendulum   & 2 & 8,8 & 13.2\,s & 6,10 & 16.6\,s\\
% Regulator   & 5 & 8,8 & 1532.7\,s & 6,10 & 999.6\,s\\
% Springmassdamper & 2 & & ~\xmark &6,10 & 24.2s \\
% Steamdrum   & 3 & 8,8  & 700.9s & 6,10 & 24.4\,s \\
% Suspension  & 4 & 8,8  & 11.4\,s & 6,10 &15.4\,s \\
% Tapedriver   & 3 & 8,8  & 11.4\,s &6,10 & 13.3\,s \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Synthesis times for fixed- and floating-point controllers\label{tab:results}}
\end{table*}

The mean run-time for the successful benchmarks is 225\,s for fixed-point and 125\,s for floating-point implementations, respectively.  
The median run-time for the successful benchmarks is 15.7\,s for fixed-point and 17.8\,s for floating-point implementations, respectively.
We consider these times to be short enough to be of practical use to control engineers, and thus assert the success of 
%EG1. 
the overall objective of the study that we have raised above.

>>>>

The CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
of the closed-loop control model model into its internal representation (IR).  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT/SMT solver to address verification checks.  We~model the 
effects of finite-precision arithmetic 
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included into
CBMC~5.7 and is available for 
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
We have further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script, 
with instructions to run all benchmarks and to reproduce our
experiments.\footnote{\url{http://www.cprover.org/DSSynth/journal.tar.gz}}
%
%\textcolor{red}{This paragraph needs to be updated by Elizabeth and Dario.}
%
%The entire implementation consists of $XXX$ and $XXX$ lines of C code in the multi-stage and abstract
%accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
%fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
%module in CEGIS CBMC.  We evaluate \tool~using $XXX$ SISO control system
%benchmarks.

@@

\begin{table*}
\centering
\begin{tabular}{| l | c | c | c| r | c | r | c |}
%
\hline
% \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
 Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time(s) & k & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time(s)  & k\\\hline
Bioreact	&	2	&	8,8	&	15.35 & 4	&	10,6	&	23.76 & 2	\\
Chen	    &	3	&	8,8	& 	11.24& 0	&	10,6	&	14.25 & 0	\\
%Chen 2	    &	3	&	8,8	&	11.24	&	10,6	&	14.25	\\
Cruise    	&	1	&	8,8	&	11.03	& 0&	10,6	&	11.17& 0	\\
Cruise 2	&	1	&	8,8	&	9.93 & 0	&	10,6	&	10.54 & 0	\\
Cst  	&	3	&	12,12	&	90.03 & 2	&	10,6	&	321.12 & 2	\\
Cstrtmp	    &	2	&	8,8	&	18.56 & 2	&	10,6	&	16.99 & 2	\\
DC motor	&	2	&	8,8	&	10.34 & 0	&	10,6	&	12.32 & 0	\\
Helicopter	&	3	&	16,16	&	1116.08 & 2	&	10,6	&	168.43 & 38	\\
Inverted %
pendulum	&	2	&	12,12 &	16.01&	2 &	10,6	&	18.73 &0	\\
Magnetic %
pointer	    &	3	&	12,12	&	1071.02	 & 10 &	10,6	&	207.60 & 9	\\
Magnetic %
suspension	&	3	&	20,20	&	56.9 & 2	&	10,6	&	998.3 & 6	\\
Pendulum	&	2	&	8,8	&	11.74 & 0	&	10,6	&	13.69 & 0	\\
Regulator	&	5	&		&	~\xmark	&  & 10,16	&	190.28	& 2 	\\
Satellite	&	2	&	8,8	&	13.91 & 3	&	10,6	&	16.92	& 7\\
Spring-%
mass-damper	&	2	&	12,12	&	16.09&	0  &	10,6	&	23.21 & 4	\\
Steam drum	&	3	&		&	~\xmark	&	& 10,16	&	21.16	& 4\\
Supension	&	4	&	8,8	&	12.40	& 5 &	10,6	&	17.03 & 5	\\
Tape driver	&	3	&	8,8	&	12.18 & 0	&	10,6	&	14.34	& 0\\
USCG tampa	&	3	&	12,12	&	1143.35 & 10 	&	10,6	&	210.70 & 9	\\
% 
%%1  & Acrobot     & 4 & 8,8 & 61529.8\,s &  & ~\xmark \\
%% Antenna     & 6 &  & ~\xmark & 6,10 & 817.4\,s \\
%%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
% Bioreact    & 3 & 8,8 & 15.3\,s & 6,10 &23.6\,s \\
%% 
% Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 14.3\,s \\
%%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
%% Chen\_ex3   & 7 & 8,8  & 11.4\,s & 6,10 & 59.1\,s \\
%%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
% Cruise      & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s \\
%% CruiseHSCC & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s  \\
% Cstr & 3 & & ~\xmark & 6,10 & 21.4\,s \\
% Cstrtmp  & 3 & 8,8 & 12.5\,s &6,10 & 15.4\,s \\
% DCmotor   & 2 & 8,8  & 10.0\,s & 6,10 & 11.4\,s  \\
%%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
%%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
% Helicopter   & 3 &  & ~\xmark & 6,10 & 32.0\,s \\
%%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
% Invpendulum\_pendang & 2 & 8,8  & 10.7 & 6,10 & 14.8\,s\\
% Magpointer   & 2 &  & ~\xmark & 6,10 & 86.0\,s \\
% Magsuspension  & 2 & 12,12  & 39.0\,s  & 6,10 & 43.2\,s \\
% Pendulum   & 2 & 8,8 & 13.2\,s & 6,10 & 16.6\,s\\
% Regulator   & 5 & 8,8 & 1532.7\,s & 6,10 & 999.6\,s\\
% Springmassdamper & 2 & & ~\xmark &6,10 & 24.2s \\
% Steamdrum   & 3 & 8,8  & 700.9s & 6,10 & 24.4\,s \\
% Suspension  & 4 & 8,8  & 11.4\,s & 6,10 &15.4\,s \\
% Tapedriver   & 3 & 8,8  & 11.4\,s &6,10 & 13.3\,s \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Synthesis times for fixed- and floating-point controllers\label{tab:results}}
\end{table*}

The mean run-time for the successful benchmarks is 225\,s for fixed-point and 125\,s for floating-point implementations, respectively.  
The median run-time for the successful benchmarks is 15.7\,s for fixed-point and 17.8\,s for floating-point implementations, respectively.
We consider these times to be short enough to be of practical use to control engineers, and thus assert the success of 
%EG1. 
the overall objective of the study that we have raised above. \rev{The completeness threshold depends upon the controller
selected, and the SAT/SMT solver picks a controller with a low completeness threshold for all the time discretisations that we solve.
The completeness threshold is zero where the controller synthesised results in a system with real valued eigenvalues.}
